---
title: "Notes-block Example"
format: pdf
header-includes:
   - \usepackage{setspace}
filters:
  - notes-block
cap-location: top
---

## Output with notes

This filter makes it easy to have figure and table notes. For example for @tbl-test and @fig-test.

:::: {#tbl-test tbl-pos="h" tbl-cap="This is a table"}

```{r}
#| echo: false
#| warning: false

library(gt)
head(mtcars) |> gt()
```

::: {.notes-block}
**Notes:** These are cars and the table notes are the default.
:::
::::

Here is some explanation on what you did here.

:::: {#fig-test fig-pos="h" fig-cap="This is a figure"}

```{r}
#| echo: false
#| warning: false

library(ggplot2)
df <- data.frame(x = 1:10, y = (1:10)^2)
ggplot(df, aes(x, y)) + 
  geom_line() +
  theme_minimal()
```

::: {.notes-block width = "0.4" above = "-3" below = "10"}
**Notes:** This plot shows the quadratic relationship between x and y. Also, the settings for the notes are different from the default. We can also use the standard referencing for example if this would be somehow related to @tbl-test.
:::
::::

